Discussion Draft

### 2020-04-08 doc/Discussion.rmd
notes for consequences

@@

@@

@@

@@

>>>>

# -- counter points, whats the consequence of reverse heterochiasmy (rapid male evolution in gwRR), 
# -- sex-average / species average of gwRR is higher (for these strains)
# --

@@

# consequence of greater female variance -- (between cell)
#

@@

# consequences of conserved typical landscape
# (sardel kirkptarick - the rec landscape -- diviation from uniform is due to male rec landscape
# (female CO suppresion -- DSB (repaired as NCO -- elevated DsB (halldorsson?))  )
#

@@

# consequences of longer female axis - 
# (normalzed interference strength due to axis differences / Chromtain loop length)
#

@@

# consequence of rapid evolution of normalized interference strength,
# in the 3 strains -- larger linkage blocks?
# but what if the rec pattern is repeated?
